Supporting Information : Effect of copula on extinction risk

### 2019-03-05 SuppMat.Rmd
adding nonlinear age str results for C,SC,G,SG

@@

<!--Supp. FIG :  age structure model results for C, SC, G, SG with linear model (\Omega = infinity)-->
\begin{figure}[!h]
\textbf{ \hspace{6.8 cm} (A) \hspace{4.4 cm} (B)} \\
\vspace{-0.9 cm}
\begin{center}
\includegraphics[width=5 cm]{./Results/age_str_results/extrisk_age_str_C_SC_linear.pdf}
\includegraphics[width=5 cm]{./Results/age_str_results/extrisk_age_str_SG_G_linear.pdf}\\
\caption{Extinction risk from single patch age structured linear ($\Omega = \infty$) models, fecundity of adults and survival of eggs have either left or right tail dependence in their corresponding copula structure $(A)$ Clayton and Survival Clayton (parameter = 3), $(B)$ Survival Gumbel and Gumbel (parameter = 2.5), numsims=10000. All copula has same Kendall correlation $\tau = 0.6$. \label{fig_extrisk_agestr_C_SC_G_SG_linear}}
\end{center}
\end{figure}

>>>>

```{r sim_nonlinear_C_SC_G_SG, echo=F,  cache=T, cache.extra=list(seed,mtime("ext_risk_cop_age_str.R"))}
set.seed(seed)
source("ext_risk_cop_age_str.R")

numsims<-10000
numsteps<-100
p0<-c(5,10)
ext_thrs<-2
gshape<-2
gscale<-1
bshape1<-3
bshape2<-2
par_dist<-c(gshape,gscale,bshape1,bshape2)
omg<-100
ktau<-0.6  # kendall's tau

tempo<-paste("./Results/age_str_results/",BiCopName(family=fam),"_par_",par,"_ktau_",ktau,"_nonlinear",sep="")
if (!dir.exists(tempo)){
  dir.create(tempo)
}

```{r fig_agestr_C_SC_G_SG_nonlinear, echo=F,results="hide"}
xL<-C_age$extdf[1:26,]
xR<-SC_age$extdf[1:26,]
t<-c(0:(nrow(xL)-1))
pdf(paste("./Results/age_str_results/extrisk_age_str_C_SC_nonlinear_omg_",omg,".pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(0,-1,ylim=c(0,1),xlim=range(t),ylab="Extinction risk",xlab="time",cex.lab=2,cex.axis=1.5)
x<-xL
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(1,0,0,0.3), border = NA)
lines(t,x$erA,col="red",type="l")
x<-xR
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(0,0,1,0.3), border = NA)
lines(t,x$erA,col="blue",type="l")
legend("topleft", c("vital rates : LTdep., C","vital rates : RTdep., SC"), lty=c(1,1),  
       col=c('red', 'blue'), horiz=F, bty='n', cex=1.5)
par(op)
dev.off()

xL<-SG_age$extdf[1:26,]
xR<-G_age$extdf[1:26,]
t<-c(0:(nrow(xL)-1))
pdf(paste("./Results/age_str_results/extrisk_age_str_SG_G_nonlinear_omg_",omg,".pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(0,-1,ylim=c(0,1),xlim=range(t),ylab="Extinction risk",xlab="time",cex.lab=2,cex.axis=1.5)
x<-xL
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(1,0,0,0.3), border = NA)
lines(t,x$erA,col="red",type="l")
x<-xR
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(0,0,1,0.3), border = NA)
lines(t,x$erA,col="blue",type="l")
legend("topleft", c("vital rates : LTdep., SG","vital rates : RTdep., G"), lty=c(1,1),  
       col=c('red', 'blue'), horiz=F, bty='n', cex=1.5)
par(op)
dev.off()
```

@@

<!--Supp. FIG :  age structure model results for C, SC, G, SG with linear model (\Omega = infinity)-->
\begin{figure}[!h]
\begin{center}
\textbf{ \hspace{0.5 cm} (A) \hspace{4.4 cm} (B)} \\
\vspace{-0.2 cm}
\includegraphics[width=5 cm]{./Results/age_str_results/extrisk_age_str_C_SC_linear.pdf}
\includegraphics[width=5 cm]{./Results/age_str_results/extrisk_age_str_SG_G_linear.pdf}\\
\textbf{ \hspace{0.5 cm} (C) \hspace{4.4 cm} (D)} \\
\vspace{-0.2 cm}
\includegraphics[width=5 cm]{./Results/age_str_results/extrisk_age_str_C_SC_nonlinear_omg_100.pdf}
\includegraphics[width=5 cm]{./Results/age_str_results/extrisk_age_str_SG_G_nonlinear_omg_100.pdf}\\
\caption{Extinction risk from single patch age structured models, fecundity of adults and survival of eggs have either left or right tail dependence in their corresponding copula structure $(A)$ Clayton and Survival Clayton (parameter = 3), $(B)$ Survival Gumbel and Gumbel (parameter = 2.5) for linear model ($\Omega = \infty$), numsims=10000. $(C - D)$ represents the analogous figures as of $(A - B)$ but for non-linear model ($\Omega = 100$). All copula has same Kendall correlation $\tau = 0.6$. \label{fig_extrisk_agestr_C_SC_G_SG_linear}}
\end{center}
\end{figure}
